\documentclass[10pt,a4paper]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{amstext}
\usepackage{url}
\usepackage[table]{xcolor}
\usepackage[font=scriptsize, center]{caption}



\title{File Sharing Program}
\author{R. van Tonder, 15676633 \\ A. Esterhuizen, 15367940}
\date{\today}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage

\section{Description}
%R
\paragraph{} 

\section{Features}
\subsection{Included}
\subsubsection{Server}
%R
The server has the following capabilities, in accordance with the
project specification.

\begin{enumerate}
 \item The server accepts connection requests from clients, and updates the user-list with the host-name of connected clients.
 \item When clients wish to initiate a voice conversation, the server responds with the appropriate host-name of the recipient. 
In this manner clients receive permission to call other hosts.
 \item Informs clients if a call or conference is already active between hosts.
 \item The server relays all messages to all clients, if they are not recognized as a command such as \verb|\call|. See \ref{det} for more.
 \item Multiple users can connect simultaneously.
 \item Whispering and global chat message relaying.
 \item Call and conference channels. This is done by keeping a list of current active calls and conferences. See \ref{det} for more.
 \item A GUI which displays 
 \begin{itemize}
  \item All messages sent through the server
  \item Client connections to the server
  \item Client disconnections from the server
  \item The current user-list
  \item Responses to commands received by the server
 \end{itemize}

\end{enumerate}

\subsubsection{Client}
The client has the following capabilities, in accordance with the project specification.

%list client features
%A
\begin{enumerate}
 \item Clients may connect and disconnect without incident.
 \item Commands that are processed by the server for various functionalities, such as \verb|\call|, \verb|\callc|, and \verb|\msg|. See \ref{det} for more.
 \item Initiating voice transmission when in a call with another host.
 \item Playing Voice output and receiving Mic input.
 \item A GUI which displays
 \begin{itemize}
  \item The current user-list
  \item All global messages, and whispers when applicable
  \item Whether a call has been initiated with the client
  \item Whether a call cannot be established, if a host is already in a conference or call.
 \end{itemize}

\end{enumerate}

\subsection{Features Not Included}
\paragraph{}
%R
%same name??

\subsection{Extra Features}
%R
% security
% pyqt
% chat functionality/gui/etc

\section{Design}
\label{det}
\subsection{Server}
%R
%keys/communication
%searching
%
\subsection{Client}
%R
%------------------
%security
%key checks
%Searcher
%---------------

%A
%--------------------------
%Downloader class
%Uploader class
%file writing/sending
%--------------------------

\section{Complications}
\label{comp}
%R
%filenames?
%downloading from same person

%A
%pause resume speed
% cables?

\section{Conclusion}
%arne


\end{document}
